Baseline centering problem

### 2018-12-12 paper/tangotd.tex

Let us assume that we have a model $\tilde P$ of the operator $P$. Thus
we can sample $\transp{\tilde \Delta}\rho \Delta$ (just sample one
transition $s\to s'$ from $\rho P$, and a second transition $s\to \tilde
s'$ from the same $s$). We can also sample from $\transp{\tilde
\Delta}\rho R$. Moreover, \emph{if rewards during $s\to s'$ are
independent from $s'$}, we can sample from $\transp{\Delta}\rho R$. From
now on, I will assume that the reward collected during a transition $s\to
s'$ depends only on $s$. \footnote{This means the state $s$ is a
sufficient statistic. If the reward depends only on $s'$ instead, we can
just
shift the rewards by one step and pretend they are collected at the next
step; therefore we are back to a reward that depends only on $s$. The
only case not covered is if the reward really depends on the pair
$(s,s')$; in that case, the state $s'$ is not quite a sufficient
statistic of the process.

In the latter case, one would also need a model $\tilde R$ of rewards,
and then we could sample from $\transp{\tilde \Delta}\rho R$ and from
$\transp{\Delta}\rho\tilde R$.}

>>>>

Let us assume that we have a model $\tilde P$ of the operator $P$. Thus
we can sample $\transp{\tilde \Delta}\rho \Delta$ (just sample one
transition $s\to s'$ from $\rho P$, and a second transition $s\to \tilde
s'$ from the same $s$). We can also sample from $\transp{\tilde
\Delta}\rho R$, by sampling a reward during $s\to s'$ from the true
model, and a simulated second
transition from $s$. Note that this does not use a model of rewards, only of
transitions.
\footnote{
Moreover, \emph{if rewards during $s\to s'$ are
independent from $s'$}, we can sample from $\transp{\Delta}\rho R$. 
(This also covers the case where rewards depend only on $s'$, by shifting
rewards by one step.) Not covered is the case where the rewards really
depends on the pair
$(s,s')$ (in that case, the state $s'$ is not quite a sufficient
statistic of the process); then we could have a model $\tilde R$ of rewards and
sample from $\transp{\Delta}\rho \tilde{R}$.

Anyway we will not assume any of this: just using
$\transp{\tilde
\Delta}\rho R$ serves our purpose.}
